FIXME

### 2013-08-29 writeups/proposal/proposal.tex
foo
Former-commit-id: 09e4866ec8c648dee8a89ac5244d61d99e726879 [formerly b0fef70c4733fdec6b003b04109efb764f6c22ef]
Former-commit-id: 2baa3d0c9b9571dd334bc0415e0a8ee69692193a

\textcite{Farahat2004} introduced the Pointwise Mutual Information (PMI) index that also measures strength of association between two terms.
It is based on the co-occurrence count between pair-wise observations of terms, similar to ACT-R's strength of association.
The PMI index is included in Equation \eqref{eqPMI}.

@@

This PMI equation is identical to ACT-R's strength of association ($S_{ji}$) equation for large datasets.
Once the number of occurrences is large enough such that the probability of observing any particular contextual element ($p(x)$) is near zero, then ACT-R's strength of association index simplifies to the PMI equation.

@@

The SNIF-ACT framework is also based on the large-scale version of $S_{ji}$, and scales well when working with a large-scale search query database for internet search \parencites{Fu2007,Pirolli2003}.
The $S_{ji}$ values were based on a 118GB local database of 10 million pages of the Stanford Webbase Project.
So this implementation did not fit into RAM, but a spinning-disk database implementation still scaled well enough for reasonably fast retrieval times for $S_{ji}$ values.

>>>>

Pointwise Mutual Information (PMI) is a another co-occurrence index that measures strength of association between two terms \parencite{Farahat2004}.
It is based on the co-occurrence count between pair-wise observations of terms, similar to ACT-R's strength of association.
The PMI index is included in Equation \eqref{eqPMI}.

@@

Further, this PMI equation is identical to ACT-R's strength of association ($S_{ji}$) equation for large datasets.
Once the number of occurrences is large enough such that the probability of observing any particular contextual element ($p(x)$) is near zero, then ACT-R's strength of association index simplifies to the PMI equation.

@@

The SNIF-ACT framework is also based on the large-scale version of $S_{ji}$, and scales well when working with a large-scale search query database for internet search \parencites{Fu2007,Pirolli2003}.
The $S_{ji}$ values were based on a 118GB local database of 10 million pages of the Stanford Webbase Project \parencite{Farahat2004}.
So this implementation did not fit into RAM, but a spinning-disk database implementation still scaled well enough for reasonably fast retrieval times for $S_{ji}$ values.
